An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-04 indicators/paper/paper.tex
Edit text around Fig 7

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/vaccine-intent-compare.pdf}
  \caption{CTIS estimates of the percentage of people willing to get vaccinated
    on January 20, 2021, compared to CDC reporting of the percentage of people
    vaccinated in each county by July 20, 2021. Points are colored by the United
    States Census region containing each county. Restricted to counties with at
    least 250 survey responses from January 14--20, 2021.}
  \label{fig:vaccine-intent-compare}
\end{figure}

As an illustration, Figure~\ref{fig:vaccine-intent-compare} illustrates how CTIS
results in January 2021, based on an item asking survey respondents whether they
would accept a COVID-19 vaccine if one were vaccinated today, predicted actual
uptake of COVID-19 vaccines by July 2021 (as reported by the Centers for Disease
Control and Prevention). It also illustrates a geographical disparity: in the
Northeast, actual vaccination rates more closely match vaccine acceptance in
January than they do in the South, where vaccination rates lag overall. While
these results must be interpreted carefully due to potential sampling biases in
the survey, they illustrate the potential of data in the COVIDcast API to inform
public health decision-making.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/vaccine-intent-compare.pdf}
  \caption{CTIS estimates of the percentage of people willing to get
    vaccinated, back on January 20, 2021, compared to CDC reporting of the  
    percentage of people vaccinated, on July 20, 2021. Each point is a county
    (with at least 250 survey responses between January 14--20, 2021), colored
    by its parent United States Census region.}     
  \label{fig:vaccine-intent-compare}
\end{figure}

As an illustration, Figure~\ref{fig:vaccine-intent-compare} illustrates how CTIS
results in January 2021, based on an item asking survey respondents whether they
would accept a COVID-19 vaccine if one were vaccinated today, predicted actual
uptake of COVID-19 vaccines by July 2021 (as reported by the Centers for Disease
Control and Prevention). It also reveals a geographical disparity: in the
Northeast, actual vaccination rates more closely match vaccine willingness rates
in January than they do in the South, where vaccination rates lag overall. While 
these results must be interpreted carefully due to potential sampling biases in
the survey, they illustrate the potential of data in the COVIDcast API to inform
public health decision-making.
